Automated Program Verification and Synthesis of Embedded \& Cyber-Physical Systems: Advances and Challenges

### 2018-02-23 paper.tex
improved introduction of section 3
Signed-off-by: Lucas Cordeiro <lucasccordeiro@gmail.com>

\textcolor{blue}{Due to the advent of sophisticated SMT solvers built over efficient SAT solvers, an increasingly number of software verifiers and synthesizers are being developed in the literature, in order to improve  productivity and produce efficient implementations for a ECPS design specification. Here, we describe recent advances in symbolic model checking of software, including BMC, \textit{k}-induction, and Craig interpolation techniques. This section also overviews software synthesis techniques that also use logic to describe states and transformations between system states.}

>>>>

\textcolor{blue}{Due to the advent of sophisticated SMT solvers built over efficient SAT solvers, an increasingly number of software verifiers as well as synthesizers have emerged in the literature, in order to verify design correctness and produce reliable implementations for ECPS. Here, we describe some achievements in symbolic model checking of software, including BMC, \textit{k}-induction, ``property-based reachability'' (or IC3), and Craig interpolation, which are currently used to the safety verification of ECPS. This section also overviews software synthesis techniques that are applicable to write correct-by-construction implementations of ECPS.}
